Ellipsoids (v1.0): 3D Magnetic modelling of ellipsoidal bodies

### 2017-04-20 manuscript/manuscript.tex

All the code developed for generating the results presented in the following
subsections, as well as the code developed for generating additional numerical simulations,
can be found at the folder \textit{code} of the repository
\url{https://github.com/pinga-lab/magnetic-ellipsoid}.

@@

The code used for generating the results presented in this section
can found at \url{https://github.com/pinga-lab/magnetic-ellipsoid/code}

>>>>

All the code developed for generating the results presented in the following
subsections, as well as the code developed for generating additional numerical simulations,
can be found at the folder \textit{code} of the online repository
\url{https://github.com/pinga-lab/magnetic-ellipsoid}.

@@
